---
title: "A brief note on colour palette"
draft: true
date: 2023-03-16
author:  
  - name: "Carlos Cámara-Menoyo"
      # given: "Carlos"
      # family: "Cámara-Menoyo"
      # literal: "Carlos Cámara-Menoyo"
    orcid: 0000-0002-9378-0549
    email: carlos.camara@warwick.ac.uk
    affiliations:
    - name: University of Warwick
      address: Centre for Interdisciplinary Methodologies (CIM), Social Sciences Building
      city: Coventry
      postal-code: CV4 7AL
categories:
  - R
  - tutorial
  - maps
format:
  html:
    toc: true
    #code-line-numbers: true
    reference-location: margin
editor: visual
bibliography: references.bib
citation: true
---

### Adding colour

We could add colours to those visualisations, but we need to understand how colours work.

First, define our color palette. We will be using [`{colorspace}`](https://colorspace.r-forge.r-project.org/articles/colorspace.html) package[^1], which provides a series of colour palettes, each of them aimed at different use cases:

[^1]: Another alternative could be using [RColorBrewer](https://renenyffenegger.ch/notes/development/languages/R/packages/RColorBrewer/index), which implements colorbrewer palettes, which are used a lot in maps: <https://colorbrewer2.org>

-   Diverging
-   Sequential
-   Diverging

```{r}
library(colorspace)

hcl_palettes(plot = TRUE, type = "Qualitative")
hcl_palettes(plot = TRUE, type = "Sequential")
hcl_palettes(plot = TRUE, type = "Diverging")

```

It seems that the colour palette that the original stripe is using is a diverging palette, and most specifically a Blue-Red variation, probably closer to `Blue-Red 3`

#### Defining colour breaks

In turn, each palette can have different number of colour breaks:

```{r}
par(mfrow = c(3, 1))
hcl_palettes(plot = TRUE, type = "Diverging", palette = "Blue-Red 3")
hcl_palettes(plot = TRUE, type = "Diverging", palette = "Blue-Red 3", n = 7)
hcl_palettes(plot = TRUE, type = "Diverging", palette = "Blue-Red 3", n = 9)
```

Now we
